\input{./preamble.tex}

\newcommand*{\mytitle}{Disease Detection in Sugar beet Plant Leaves} % Titel
\newcommand*{\myinstitute}{Department Lippstadt 2} % Institut


\newcommand*{\myauthor}{Olaniyi Bayonle Alao} % Autoren
\newcommand*{\myreporttype}{Project Work} % Bericht-Typ
\newcommand*{\mygraduation}{Bachelor of Engineering} % Vollständige Anschrift



\newcommand*{\firstexaminer}{Prof. Dr. Stefan Henkler} % Ort
\newcommand*{\secondexaminer}{Dipl.-Wirt.-inf. Kristian Rother} % Ort
\newcommand*{\mydate}{\today} % Datum


% ============= Dokumentbeginn =============

\begin{document}

% Seiten ohne Kopf- und Fußzeile sowie Seitenzahl
\pagestyle{empty}

\include{01_titel}	% Einbinden der Titelseite
\newpage 					% Um Seite nach der Titelseite einzubinden -> bei eigener Titelseite und nicht der Latex-Version erforderlich
\thispagestyle{empty}
\quad 
\newpage
\pagenumbering{Roman}
 
\cleardoubleoddpage

% ✅✅✅
\newpage
 \section*{Abstract}
 Various diseases diminish the quantity and quality of crops during the harvest season, diseases like Cercospora leaf spot (CLS) amount to a 50\%yield loss for sugar beet. Conventional disease detection and classification methods are through visual inspections by experts and laboratory tests of plant leaves or soil samples. However, these traditional methods are tedious and time-consuming. Hence, machine learning methods for the automatic detection of plant leaf diseases have been investigated in works of literature. This paper reviews two sensing methods: colour imaging and hyperspectral imaging to detect and monitor leaf disease. First, this review briefly presents the introduced sensing techniques and machine learning methods. It then provides an overview of studies using machine learning and CNN architectures for leaf disease detection in sugar beets. Finally, the paper concludes by suggesting future works in automatic leaf disease detection in sugar beet under precision farming.



\tableofcontents			%Inhaltsverzeichnis


%\chapter*{Abkürzungsverzeichnis}
%	\begin{acronym}[4GDH]	% Zur Formatierung hier die längste Abkürzung des Verzeichnisses eintragen
%		\acro{4GDH}{4th Generation District Heating} 	
%	\end{acronym}

\pagestyle{fancy}

\input{cha/01Introduction}%link to chapters

\input{cha/02Common_Diseases_in_sb}

\input{cha/03Disease_Asses_Sensors}

\input{cha/04Analysis}

\input{cha/05conclusion}

%Literaturverzeichnis
\newpage
\lhead{}
\rhead{\leftmark}
\addcontentsline{toc}{chapter}{References}

\bibliography{References}
\bibliographystyle{alpha}


\listoffigures				%Verzeichnis aller Bilder
\listoftables				%Verzeichnis aller Tabellen
%list of definitions, ...

\chapter*{Affidavit}
I \myauthor herewith declare that I have composed the present paper and work by myself and without use of any other than the cited sources and aids. Sentences or parts of sentences quoted literally are marked as such; other references with regard to the statement and scope are indicated by full details of the publications concerned. The paper and work in the same or similar form has not been submitted to any examination body and has not been published. This paper was not yet, even in part, used in another examination or as a course performance.
. ~\\
Lippstadt,  \today\\[.6cm] %<city>, <date>
\myauthor\\ % signature
\rule[0.5em]{20em}{0.5pt}

\appendix

\include{cha/08Appendix}

\end{document}
